Consensus in the Browser using WebRTC

### 2020-06-12 paper/main.tex
final submission

When a peer seeks to establish an WebRTC connection, it first gathers information on how other peers may route packets to it. This information, known as an ICE (Interactive Connectivity Establishment) candidate, is then sent to the target peer via the known relay server. Upon receiving an ICE candidate, the receiving peer registers that information, seeks out its own ICE candidates, and relays them back to the sending peer. At this point, both peers have the necessary knowledge to establish a direct peer-to-peer connection.

@@

Upon receiving a \textit{discover} message from the signaling server, the node then creates an SDP and forwards that via the signaling server to each newly discovered node.

@@

\subsection{Byzantine Fault Tolerance}
Raft is not a byzantine fault tolerant consensus algorithm. However, the nature of achieving consensus in a user's browser exposes the algorithm to attacks from untrusted parties. While this can be mitigated with digital signing of RPCs, the cryptographic operations necessary would noticeably affect the latency of the system, as web browsers are still developing performant support for cryptography.

>>>>

When a peer seeks to establish a WebRTC connection, it first gathers information on how other peers may route packets to it. This information, known as an ICE (Interactive Connectivity Establishment) candidate, is then sent to the target peer via the known relay server. Upon receiving an ICE candidate, the receiving peer registers that information, seeks out its own ICE candidates, and relays them back to the sending peer. At this point, both peers have the necessary knowledge to establish a direct peer-to-peer connection.

@@

Upon receiving a \textit{discover} message from the signaling server, the receiving node then creates an \textit{offer} containing its SDP and forwards that via the signaling server to each newly discovered node.

@@

\subsection{Byzantine Fault Tolerance}
Raft is not a byzantine fault tolerant consensus algorithm. However, the nature of achieving consensus in a user's browser exposes the system to attacks from untrusted parties. While this can be mitigated with digital signing of RPCs, the cryptographic operations necessary would noticeably affect the latency of the system, as web browsers are still developing performant support for cryptography.
